---
title: "Activity: Street or Road?"
author: "DEEKSHITH REDDY BHOOMIREDDY"
output: html_notebook
---

## Load in the data

```{r}
#load libraries 
library(dplyr)
library(tidyverse)

#load in the data here 
# we will only be using the "street-addresses.csv" file from the text
download.file(url = "https://mdbeckman.github.io/dcSupplement/data/CMS_ProvidersSimple.rds",
              destfile = "Your-Name-For-The-File.rds")
DataTable <- readRDS("Your-Name-For-The-File.rds")


```

## Recreate Solved Example using `sample(50)`

```{r}
Addresses <- read_csv("https://mdbeckman.github.io/dcSupplement/data/street-addresses.csv")
Sample <- 
  Addresses %>%
  sample_n(size = 50)

```

## Recreate Soved Example using the entire `Address` data set

```{r}
pattern <- "BOX\\s+(\\d+)"

Matches <- 
  Sample %>% 
  filter(grepl(pattern, address))

Don <-
  Sample %>%
  filter( !grepl(pattern, address))

```

#### Additional Question: How many addresses are a PO BOX (including NCSU BOX)? 

```{r}
Matches <- 
  Sample %>% 
  filter(grepl(pattern = "PO BOX|NCSU BOX", address)) %>% 
  nrow()

Matches

```

My answer here...... 


## Back to the Streets: Your Turn

#### Part 1: Explain (in english) each line of the following code chunk

```{r}
pattern <- "(ST|RD|ROAD)"
LeftOvers <-
  Addresses %>% 
  filter( !grepl(pattern, address),
          !grepl("\\sAPT|UNIT\\s[\\d]+$", address),
          !grepl(" BOX ", address)
          )
```

My answer here.......

pattern <- "(ST|RD|ROAD)": This line stores "(ST|RD|ROAD)" in the variable pattern, but this will later be used to match and filter out the street endings with "ST", "RD", "ROAD".

LeftOvers <-: It is a variable called "LeftOvers" in which the code below this is stored.

Addresses %>% : This initiates the "Addresses" data set and passes the output to the filter function in the next line using the pipe operator

filter( !grepl(pattern, address),: Filters out the address that matches the data stores in the pattern variable or simply it filter out the street endings with "ST", "RD", "ROAD".

!grepl("\\sAPT|UNIT\\s[\\d]+$", address),: This filters out the addresses ending with "APT" or "UNIT" and followed by digits

!grepl(" BOX ", address): Filters out address that contain this- " BOX ".

#### Part 2: Implement your method on the entire `Addresses` data set. Explain how your code works line by line.

```{r}



```

My answer here.......

#### Additional Question 1: Present your result from part 2 by providing a table in descending order of popularity for the street name endings you found

```{r}


```

#### Additional Question 2: Present your result by using ggplot to a bar chart in descending order of popularity for the street name endings you found previously.

Note: make sure your order street names according to popularity, not alphabetically.

```{r}

```

#### Additional Question 3: Comment on any patterns you see

My answer here.......
